---
title: "Boston Listings Project"
authors: "Fahad Aloqayli, , "
date: "`r Sys.Date()`"
output: 
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r init, include=F}
library(ggplot2)
library(ezids)
library(readr)
library(dplyr)
listings <- read_csv("listings.csv")

```


```{r setup, include=FALSE}
knitr::opts_chunk$set(results="markup", warning = F, message = F)
options(scientific=T, digits = 3) 
```

# Introduction 


```{r}
colnames(listings)
sum(is.na(listings$neighbourhood_group))


hist(listings$price, main = "Histogram of Listing Prices", xlab = "Listing Price")
boxplot(listings$price, main = "Boxplot of Listing Prices", ylab = "Listing Price")


listings_no_rm  <- outlierKD2(listings, price)               
listings_clean  <- outlierKD2(listings, price, rm = TRUE)     

```



## Q1- How does the price per Boston listing on AirBnB differ by neighborhood from June 2024 to June 2025?




## Q2- How do prices on AirBnB for Boston listings differ between listings for shared rooms versus entire homes in June 2024 to June 2025?



## Q3- How do prices differ in Boston for AirBnB listings between geographic location, using the given latitude and longitude points, between June 2024 and June 2025?




## Q4- Does the number of homes listed by a host impact the price of the AirBnB listing from June 2024 to June 2025?




# Conclusion 


